### 2023-11-11 manuscript/manuscript.Rmd
Update the conclusion to include the standards mixture

Using correlation networks of *m/z* feature abundances, molecular formula selection and graphical component selection, assigned molecular formulas for predicted IPs could be recovered from a subset of chemical standards spiked into an example human urine sample analysed using FIE-HRMS.
It was also possible to assign molecular formulas of common primary and secondary metabolites present in the KEGG compound database to *m/z* features from leaf tissue of *B. distachyon* using both FIE-HRMS and C18-UHPLC-HRMS profiling techniques.

>>>>

Using correlation networks of *m/z* feature abundances, molecular formula selection and graphical component selection, assigned molecular formulas for predicted IPs could be recovered from a mixture of chemical standards as well as an example human urine sample spiked with this mixture, analysed using FIE-HRMS.
It was also possible to assign molecular formulas of common primary and secondary metabolites present in the KEGG compound database to *m/z* features from leaf tissue of *B. distachyon* using both FIE-HRMS and C18-UHPLC-HRMS profiling techniques.
